`clarify`: Simulation-Based Inference for Regression Models

### 2024-05-30 clarify/Submission 2/response_to_reviewers.Rmd

> Also, what does "accurate" mean, exactly? What does "often" mean? Under what conditions, exactly? This is a paper about software, so I don't expect a full theoretical investigation. But there should be at least be a little bit more discussion and breadcrumbs for users to follow. Are there good theoretical or simulation studies on the properties of this strategy, identifying when it works better or worse? Currently, the reader might leave the paper with the impression that simulation-based inference strictly dominates the delta method and bootstrapping in all cases, except along the computational cost dimension. Is that really true? I'll freely admit that I'm a bit skeptical, but I would love to see some references to authors who probe this question. I'm sure other readers would find this useful too in deciding whether they should use `clarify`.
>
> The flip side of this question is: If simulation-based inference is easier and more accurate, why isn't everyone using it already? What's the market failure?

Thank you for this comment. We have attempted to soften the language used and provide citations for studies that have compared the performance of the delta method and simulation-based inference. Unfortunately, there are few studies comparing the two for general inference of common quantities like average adjusted predictions or average marginal effects, but for the few quantities that have been studied, simulation-based inference has competitive performance. In general, by "accurate" and "valid" we mean achieving close to nominal coverage rates.

We highlight scenarios in which each of the three methods by be expected to perform better than the others, when they might fail, and when they might be expected to agree. However, there has been insufficient research done to make strong affirmative claims recommending any approach over the others universally, and we attempt to avoid making such claims.

Although simulation-based inference may be less common nowadays, it is worth noting that King et al. (2000), which introduced to method to political scientists, is among the most highly cited political methodology articles as noted by the other reviewer, and the software packages that implement its method, `Zelig` and `CLARIFY` for Stata, have been widely used. Modern tools that implement the delta method like `marginaleffects` and `margins` in Stata are certainly the standard nowadays, but we would argue there has not been a general-purpose simulation-based inference package in R, which may have reduced its uptake. Additionally, researchers may be resistant to use a less-studied method, especially one that is computationally intensive and yields results that depend on a seed; we are sympathetic to these concerns but believe simulation-based inference should at least be available in an easy-to-use package, even if it is currently less commonly used than other methods.

@@

> ### Approximations in simulation-based inference
>
> The authors write:
>
> > Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates.
>
> This may seem trivial, taking M random draws will lead to a different result than drawing a different M' set of coefficients. Clearly, there's a simulation-related approximation going on. This should be acknowledged early in the intro. The authors should revise the text to avoid saying that simulation-based inference requires no approximation.

We have noted the approximation due to Monte Carlo error and highlight that many replications may be required for results to stabilize. We highlight that this is a disadvantage for simulation-based inference relative to the delta method.

> ### Assumption or approximation?
>
> The abstract and introduction sell simulation-based inference as a way to relax "assumptions" of the delta method, but then goes on to talk about "approximations" that may fail:
>
> > The usual method for estimating the uncertainty of the derived quantities is known as the “delta method”, which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the estimate of the derived quantity is normally distributed.
>
> The classic textbook treatment of the delta method talks about two assumptions: continuity, and normality of the $\hat{\theta}$ --- not of derived quantities $h(\hat{\theta})$. Do the authors see a distinction between a violation of delta method assumptions and a "failure" of approximations in finite samples? If so, this should be cleared up in the abstract and intro to avoid confusion.

Normality of $h(\hat\theta)$ is required for valid use of Normal quantiles for Wald-based inference of the derived quantity. Of course both simulation-based inference and the delta method require joint Normality of $\hat\theta$. We have attempted to clarify this and soften the language around assumptions and their violation. We also cite a few studies that have compared their performance for derived quantities that explicitly do not have a Normal distribution.

@@

Thank you for this comment. We have attempted to clarify this and include a footnote acknowledging this. A benefit of simulation-based inference is that as long as there exists a transformation that yields a symmetric distribution, one does not need to know what that transformation is in order for the quantile-based interval to be valid; this has been described for quantile intervals for the bootstrap, which we now reference in the paper. To keep the paper focused on the software, we have chosen not to delve too deeply into a thorough empirical comparison between the methods to highlight when either might fail.

> ### Minor notes
>
> -   Why are all functions prefixed with `sim_`? I would argue that these prefixes are extraneous, and that this is what the namespace is for.
> -   Can `plot()` draw on more dimensions if more variables are included in `sim_setx()`?
> -   It is not clear to me from the documentation what `null` values are acceptable in `summary()`. I see RD and RR. What else?
>
> > The largest difference is that clarify supports iterative building of more and more complex hypotheses through the transform() method, which quickly computes new quantities and transformation from the existing computed quantities, whereas marginaleffects only supports a single transformation
>
> Or users can call `posterior_draws()` to manipulate the draws themselves, but this is admittedly less convenient.

We prefixed functions with `sim_` to highlight that these are specifically to be used after running `sim()`. Although the namespace and class checking accomplishes this as well, removing the `sim_` prefix would leave functions like `apply()`, `adrf()`, and `ame()`, suggesting these functions are general-purpose functions for computing the relevant quantity, whereas they are specifically to be used in the context of simulation-based inference with `clarify`. This also avoid namespace clashes with other packages that might implement more general-purpose functions.

@@

Yes, `plot()` can include other variable combinations as colors or facets when used with `sim_setx()`. In practice, varying too many variables will create cluttered plots, so we highlight simpler plots in the paper as example use cases.

The user can supply any value to `null` depending on the hypothesis they want to test, if any. Often, researchers are interested in tests of no effect, which need to be defined differently for the contrast being used. For example, to test a hypothesis that two probabilities are equal, one can test whether their difference is 0, their ratio is 1, or their odds ratio is 1, etc. We do not specify which values the null should take to allow users to supply their own hypothesis. In some cases, hypothesis testing may not be of interest at all (e.g., for model predictions), so `null` can be omitted.

Although it is certainly possible to perform similar manipulations from the `marginaleffects` output, we would argue that because the focus of `clarify` is solely on simulation-based inference, its interface is more user-friendly for this analysis. `posterior_draws()` output needs to be reshaped and is better designed for expert users than casual users of the package, whereas `transform()` uses an existing base R function with a simple interface that yields an object with the same properties as the object the user started with. We would like to think `transform()` is one of the biggest contributions of this package, as it supports iterative construction of more and more complicated quantities of interest without any increase in computational time.

@@

------------------------------------------------------------------------

We thank both reviewers for their insightful comments and support for the paper and package. We hope to have improved the paper through their comments while maintaining our position that `clarify` implements useful methodology for applied researchers, and therefore would benefit the R community.

### 2025-01-23 clarify/Final version/clarify.Rmd
Package cleaning and prep for final submission

---
title: "`clarify`: Simulation-Based Inference for Regression Models"
date: "`r Sys.Date()`"
abstract: >
  Simulation-based inference is an alternative to the delta method for computing the uncertainty around regression post-estimation (i.e., derived) quantities such as average marginal effects, average adjusted predictions, and other functions of model parameters. It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form a simulated "posterior" distribution of the quantity from which confidence intervals can be computed. `clarify` provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest. `clarify` supports a large and growing number of models through its interface with the `marginaleffects` package and provides native support for multiply imputed data.
draft: true
author:  
  - name: Noah Greifer
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    url: ngreifer.github.io
    orcid: 0000-0003-3067-7154
    email:  ngreifer@iq.harvard.edu
  - name: Steven Worthington
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    email: sworthington@iq.harvard.edu
    orcid: 0000-0001-9550-5797
  - name: Stefano Iacus
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    email: siacus@iq.harvard.edu
    orcid: 0000-0002-4884-0047
  - name: Gary King
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    email: king@harvard.edu
    orcid: 0000-0002-5327-7631
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib
---

@@

## Introduction

@@

## Related Software

Similar functionality exists in the \pkg{CLARIFY} package in Stata[^2] [@tomzClarifySoftwareInterpreting2003] and used to be available in the `Zelig` R package [@imaiCommonFrameworkStatistical2008a], though there are differences in these implementations. \CRANpkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below). \CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package [@arel-bundockMarginaleffectsPredictionsComparisons2024], which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).

@@

## Using \CRANpkg{clarify}

@@

### 1. Fitting the model

@@

### 2. Drawing from the coefficient distribution

@@

### 3. Computing derived quantities

@@

-   `...` - further arguments to `FUN`.

@@

### 4. Summarize and visualize the simulated distribution

@@

## `sim_apply()` Wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`

@@

### `sim_setx()`: predictions at representative values

@@

### `sim_ame()`: average adjusted predictions and average marginal effects

@@

### `sim_adrf()`: average dose-response functions

@@

## Transforming and Combining Estimates

@@

### `transform()`

@@

### `cbind()`

@@

## Using \CRANpkg{clarify} with Multiply Imputed Data

@@

## Comparison to Other Packages

Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} [@lenthEmmeansEstimatedMarginal2024], \CRANpkg{margins} [@leeperMarginsMarginalEffects2024], \CRANpkg{modelbased} [@makowskiEstimationModelbasedPredictions2020], and \CRANpkg{marginaleffects} [@arel-bundockMarginaleffectsPredictionsComparisons2024]. Many of the quantities computed by these packages can also be computed by \CRANpkg{clarify}, the primary difference being that \CRANpkg{clarify} uses simulation-based inference rather than delta method-based inference.

@@

## Conclusion

>>>>

---
title: "`clarify`: Simulation-Based Inference for Regression Models"
date: "`r Sys.Date()`"
abstract: >
  Simulation-based inference is an alternative to the delta method for computing the uncertainty around regression post-estimation (i.e., derived) quantities such as average marginal effects, average adjusted predictions, and other functions of model parameters. It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form a simulated "posterior" distribution of the quantity from which confidence intervals can be computed. `clarify` provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest. `clarify` supports a large and growing number of models through its interface with the `marginaleffects` package and provides native support for multiply imputed data.
draft: true
author:  
  - name: Noah Greifer
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    url: ngreifer.github.io
    orcid: 0000-0003-3067-7154
    email:  ngreifer@iq.harvard.edu
  - name: Steven Worthington
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    email: sworthington@iq.harvard.edu
    orcid: 0000-0001-9550-5797
  - name: Stefano Iacus
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    email: siacus@iq.harvard.edu
    orcid: 0000-0002-4884-0047
  - name: Gary King
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    email: king@harvard.edu
    orcid: 0000-0002-5327-7631
type: package
output: 
  rjtools::rjournal_pdf_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib
---

@@

# Introduction

@@

# Related Software

Similar functionality exists in the \pkg{CLARIFY} package in Stata[^2] [@tomzClarifySoftwareInterpreting2003] and used to be available in the `Zelig` R package [@imaiCommonFrameworkStatistical2008a], though there are differences in these implementations. \CRANpkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below). \CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package [@marginaleffectsforthcoming], which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).

@@

# Using \CRANpkg{clarify}

@@

## 1. Fitting the model

@@

## 2. Drawing from the coefficient distribution

@@

## 3. Computing derived quantities

@@

-   `...` -- further arguments to `FUN`.

@@

## 4. Summarize and visualize the simulated distribution

@@

# `sim_apply()` Wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`

@@

## `sim_setx()`: predictions at representative values

@@

## `sim_ame()`: average adjusted predictions and average marginal effects

@@

## `sim_adrf()`: average dose-response functions

@@

# Transforming and Combining Estimates

@@

## `transform()`

@@

## `cbind()`

@@

# Using \pkg{clarify} with Multiply Imputed Data

@@

# Comparison to Other Packages

Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} [@emmeans2024], \pkg{margins} [@margins2021], \CRANpkg{modelbased} [@modelbased2020], and \CRANpkg{marginaleffects} [@marginaleffectsforthcoming]. Many of the quantities computed by these packages can also be computed by \CRANpkg{clarify}, the primary difference being that \CRANpkg{clarify} uses simulation-based inference rather than delta method-based inference.

@@

# Conclusion
